Binning Strategies and Related Loss for Large Data

### 2015-04-21 Paper.Rnw
Reorder distributions in scatterplot figure to match others

# plot the original data
# make rounded data find overlapping points to make plot rendering faster
dat <- rbind(datlist[[1]],datlist[[2]],datlist[[3]])
smallround <- ddply(dat,.(type,record,roundx,roundy),summarise,
      overlap = length(roundx))
smallround <-cbind(data.frame(x=smallround$roundx,y=smallround$roundy), 
                   smallround[,1:4])
smallround$record <- "Coarse"
alldat <- rbind(dat,smallround)

qplot(x,y,geom="point",data=alldat,facets=record~type, size=I(1)) + 
  theme_bw() + 
  #ggtitle("Scatterplots of Simulated Data") +
  xlab("X") + ylab("Y") + 
  scale_x_continuous(breaks=c(0,25,50,75,100)) + 
  scale_y_continuous(breaks=c(0,25,50,75,100))
@

>>>>

# plot the original data
# make rounded data find overlapping points to make plot rendering faster
dat <- rbind(datlist[[1]],datlist[[2]],datlist[[3]])
smallround <- ddply(dat,.(type,record,roundx,roundy),summarise,
      overlap = length(roundx))
smallround <-cbind(data.frame(x=smallround$roundx,y=smallround$roundy), 
                   smallround[,1:4])
smallround$record <- "Coarse"
alldat <- rbind(dat,smallround)
alldat$type <- factor(alldat$type, levels=c("Exponential","Normal","Uniform"))

qplot(x,y,geom="point",data=alldat,facets=record~type, size=I(1))+
  theme_bw() + 
  #ggtitle("Scatterplots of Simulated Data") +
  xlab("X") + ylab("Y") + 
  scale_x_continuous(breaks=c(0,25,50,75,100)) + 
  scale_y_continuous(breaks=c(0,25,50,75,100))
@
